### 2010-11-02 report/report.tex
edited report more.

\begin{itemize}
\item \emph{Team member:} Jason and Sarah.
\item \emph{Current implementation:} The user has a choice between four
  different learning strategies: uniform random hill climbing, gaussian random
  hill climbing, and N-dimensional policy gradient algorithm descent.
  \begin{itemize} 
  \item \emph{Uniform random hill climbing:} Creates a random neighbor by
  randomly choosing one parameter to adjust, and changing either
  completely randomly in UniformStrategy(), or slightly in
  UniformSlightStrategy(). Then evaluates this neighbor by running the robot
  with the newly chosen parameters. If this neighbor results in a
  longer distance walked then the previous best neighbor, we save this
  neighbor as the new best neighbor. We then repeat the whole process
  using the best neighbor as a base.
  \item \emph{Gaussian random hill climbing} Creates a random neighbor byi
  changing each parameter randomly based on a normal distribution. Then
  evaluates this neighbor similarly to uniform random hill climbing.
  \item \emph{N-dimensional policy gradient descent} Estimates the policy
  gradient by evaluating \emph{t} randomly generated policies
  near an initial parameter vector. Then computes the average score 
  \end{itemize}
\item \emph{Future improvements:} Machine learning of objective function.
\item \emph{Status:} Described algorithms coded. Machine learning of objective
  function to be coded by Jason.
\end{itemize}

@@

\begin{itemize}
\item \emph{Team member:} Jason and Diana.
\item \emph{Current implementation:} A wii remote keeps track of the
position of the robot by tracking an infrared light on the robot. 
There is a motion loop that uses own position...(Jason and Diana, write
more about this.
\item \emph{Status:} Complete.
\end{itemize}

@@

\begin{itemize}
\item \emph{9/13-9/19:} Set up. Set up trac, worked on pre-proposal
  and presentation, got lab access, met with Jim Torresen, contacted
  Juan Cristobal Zagal, read papers, got the robot to walk using
  previously coded program. Questions -- How do we move the robot? How
  do we command the motors?
\item \emph{9/20-9/26:} Moving the robot. Installed Linux on the
  robot, figured out how to command the motors, coded a program to
  make the robot stand up, coded a simple motion pattern. Questions --
  For initial program, what parameters and model should be used? How
  do we limit the search space? What algorithm should we start with?
  How will the robot get information about how far it moved?
\item \emph{9/27-10/3:} Initial program. Chose several parameters and
  created a simple parameterized sine model, implemented a random hill
  climbing algorithm to optimize the parameters, ran some trial
  iterations, began setting up the cameras for feedback. Questions --
  Did the initial program work? What parameters are important? Are
  additional parameters necessary? What algorithm should we implement
  for the final program?
\item \emph{10/4-10/5:} Plan for final implementation. Discussed
  possible algorithms to use and new parameters to add. Worked on
  report for code review \#1. Questions -- Advantages for gradient
  descent? Should we start with a completely random parameter vector
  or should we start with one that results in motion and let the
  program optimize it?
\end{itemize}

@@

\begin{itemize}
\item \code{optimize.py}: Determines a strategy to try and runs the robot
  with that strategy.
\item \code{RunManager.py}: Deals with all the details of running the robot,
  including choosing an initial parameter, running the robot multiple times, 
  tracking distance walked, and writing to the log file. Also includes the
  \code{explore\_dimensions} method.
\item \code{Strategy.py}: Contains all the different possible strategies, which
  will be passed as objects in \code{optimize.py}. 
\item \code{Robot.py}: Implements the \code{Robot} class, described in
  \secref{implement}.
\item \code{SineModel.py}: Implements a sine based motion model,
  described in \secref{implement}.
\item \code{Motion.py}: Motion helper functions.
\item \code{WiiTrackServer.py, WiiTrackClient.py}: ? Jason, write this.
\end{itemize}

>>>>

\begin{itemize}
\item \emph{Team member:} Jason and Sarah.
\item \emph{Current implementation:} The user has a choice between three
  different learning strategies: uniform random hill climbing, gaussian random
  hill climbing, and N-dimensional policy gradient algorithm descent.
  \begin{itemize} 
  \item \emph{Uniform random hill climbing:} Creates a random neighbor by
  randomly choosing one parameter to adjust, and changing either
  completely randomly in UniformStrategy(), or slightly in
  UniformSlightStrategy(). Then evaluates this neighbor by running the robot
  with the newly chosen parameters. If this neighbor results in a
  longer distance walked then the previous best neighbor, we save this
  neighbor as the new best neighbor. We then repeat the whole process
  using the best neighbor as a base.
  \item \emph{Gaussian random hill climbing} Creates a random neighbor byi
  changing each parameter randomly based on a normal distribution. Then
  evaluates this neighbor similarly to uniform random hill climbing.
  \item \emph{N-dimensional policy gradient descent} Estimates the policy
  gradient by evaluating \emph{t} randomly generated policies
  near an initial parameter vector. Then computes the average score 
  \end{itemize}
\item \emph{Future improvements:} Machine learning of objective function.
\item \emph{Status:} Described algorithms coded. Machine learning of objective
  function to be coded by Jason.
\end{itemize}

@@

\begin{itemize}
\item \emph{Team member:} Jason and Diana.
\item \emph{Current implementation:} A Wii remote tracks the location of the robot through an infrared LED mounted on top of the robot. We used CWiid library which is able to interface with the remote via bluetooth to determine the location of the infrared LED. This information is accessed through some functions we wrote and passed to the program. The program gets the robot's position at the beginning of each run and then again at the end. The program then calculates the net change in position and uses that as the distance walked.
\item \emph{Status:} Complete.
\end{itemize}

@@

\begin{itemize}
\item \emph{9/13-9/19:} Set up. Set up trac, worked on pre-proposal
  and presentation, got lab access, met with Jim Torresen, contacted
  Juan Cristobal Zagal, read papers, got the robot to walk using
  previously coded program. Questions -- How do we move the robot? How
  do we command the motors?
\item \emph{9/20-9/26:} Moving the robot. Installed Linux on the
  robot, figured out how to command the motors, coded a program to
  make the robot stand up, coded a simple motion pattern. Questions --
  For initial program, what parameters and model should be used? How
  do we limit the search space? What algorithm should we start with?
  How will the robot get information about how far it moved?
\item \emph{9/27-10/3:} Initial program. Chose several parameters and
  created a simple parameterized sine model, implemented a random hill
  climbing algorithm to optimize the parameters, ran some trial
  iterations, began setting up the cameras for feedback. Questions --
  Did the initial program work? What parameters are important? Are
  additional parameters necessary? What algorithm should we implement
  for the final program?
\item \emph{10/4-10/10:} Plan for final implementation. Discussed
  possible algorithms to use and new parameters to add. Worked on
  report for code review. Discussed feedback from code review.  Questions -- Advantages for gradient
  descent? Should we start with a completely random parameter vector
  or should we start with one that results in motion and let the
  program optimize it? How does the camera system work?
\item \emph{10/11-10/17:} Discussed how we were going to proceed with the project and set up a more detailed schedule. Got the cameras working and calibrated them. Researched the 3 available streaming protocols. Questions -- Which streaming protocol would work best? Which improvements should we start with?
\item \emph{10/18-10/24:} Created a variation on the random hill climbing algorithm to choose the next neighbor based on a Gaussian distribution. Tried to work with two of the streaming protocols for the camera system, but were unsuccessful. Decided to use a Wii remote for positional information instead. Wrote the integration code for the Wii remote. Refactored our code to separate the different algorithms. Began planning the algorithm for a modified gradient descent.
Questions -- What values should we use in the gradient descent algorithm? How much should the each parameter be changed? How many neighbors should be sampled before choosing the next state? How can we compare the results of our different algorithms? How repeatable is the distance traveled for a given parameter vector?
\item \emph{10/25-11/2}: Created a modified gradient descent algorithm. Ran 150 trials of the three algorithms. Each algorithm started with a specific parameter vector and ran for 50 iterations. Created and ran a program to get a feel for the overall look of the search space. Ran some trials to see how reproducible the distance traveled was. Prepared for code review 2. Questions -- What does the search space look like? Are there a lot of spikes, or is it fairly smooth? Based on the results of the algorithms, what conclusions can we draw?
\end{itemize}

@@

\begin{itemize}
\item \code{optimize.py}: Determines a strategy to try and runs the robot
  with that strategy.
\item \code{RunManager.py}: Deals with all the details of running the robot,
  including choosing an initial parameter, running the robot multiple times, 
  tracking distance walked, and writing to the log file. Also includes the
  \code{explore\_dimensions} method.
\item \code{Strategy.py}: Contains all the different possible strategies, which
  will be passed as objects in \code{optimize.py}. 
\item \code{Robot.py}: Implements the \code{Robot} class, described in
  \secref{implement}.
\item \code{SineModel.py}: Implements a sine based motion model,
  described in \secref{implement}.
\item \code{Motion.py}: Motion helper functions.
\item \code{WiiTrackServer.py}: Broadcasts the position of the infrared LED>
\item \code{WiiTrackClient.py}: Connects to the WiiTrackServer to get the current position information.
\end{itemize}
